Retrofitting Effect Handlers onto OCaml

### 2020-12-11 retro-concurrency.tex
Updates

Effect handlers provide a structured form of delimited
continuations~\cite{Danvy90} that enables non-local control-flow mechanisms
such as resumable exceptions, coroutines, generators and asynchronous I/O to be
composably expressed. For example, consider the task of handling
division-by-zero in a calculator application. Different calculators handle
division-by-zero differently. In the iOS 13 Calculator (|iOS|), |0/0| returns
|Error|. In the Google search calculator (|gsearch|) |0/0| returns |Error|, but
for |n!=0| the |n/0| returns |Infinity| with the same sign as |n|. How do we
capture all these different behaviours without changing the evaluator?

@@

\if{0}
\begin{enumerate}[label=R\arabic*]
	\item \textbf{Backwards compatibility} A well-behaved OCaml program does not
		break under OCaml extended with effect handlers. OCaml code that does not
		use effect handlers will pay negligible performance cost.
  \item \textbf{Tool compatibility} OCaml with effect handlers produce
    well-formed backtraces, and remains compatible with program analysis tools
    such as debuggers and profilers that inspect the stack using DWARF stack
    unwind tables.
  \item \textbf{Effect handler efficiency} In order to support
    highly-concurrent applications, the program must accommodate millions of
    continuations at the same time. Installing effect handlers, capturing and
    resuming continuations must be fast.
  \item \textbf{Forwards compatibility} While this work does not present an
    effect system, the design must be compatible with a future effect system
    for OCaml. As a cornerstone of modularity, we also want blocking I/O code
    to \emph{transparently} be made asynchronous with the help of effect
    handlers.
\end{enumerate}
\fi

>>>>

Effect handlers provide a structured form of delimited
continuations~\cite{Danvy90} that enables non-local control-flow mechanisms
such as resumable exceptions, coroutines, generators and asynchronous I/O to be
composably expressed. For example, consider the task of handling
division-by-zero in a calculator application. Different calculators handle
division-by-zero differently. In the iOS 13 Calculator (|iOS|),
division-by-zero returns |Error|. In the Google search calculator (|gsearch|)
|0/0| returns |Error|, but for |n!=0| the |n/0| returns |Infinity| with the
same sign as |n|. How do we capture all these different behaviours without
changing the evaluator?

@@
